Sizing the effects of temperature on fish - from physiology to ecology

### 2017-06-30 figures/m.Rnw
arg

<<mortality,fig.align='center',fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=4, fig.height=3,out.height=4,out.width=3>>=
  require(ggplot2)
mframe <- data.frame(tau = rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3),
                     etalab = as.character(c(0.33,1,3)),
                     M=rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3)^c(0.33,1,3)*1)

>>>>

<<mortality,fig.align='center',fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=4, fig.height=3,out.height='0.4\\textwidth'>>=
  require(ggplot2)
mframe <- data.frame(tau = rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3),
                     etalab = as.character(c(0.33,1,3)),
                     M=rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3)^c(0.33,1,3)*1)
